Spin canonical rings of log stacky curves

### 2016-01-02 curves-write-up/spin-cring.tex
Updated MONSTER LEMMA

\noindent
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.
\end{defn}

\begin{rem}
\label{rem:gorenstein}
	The log canonical ring, defined to be the direct sum of the even
	graded pieces of the log spin canonical ring, is Gorenstein. It is
	Cohen Macaulay from \cite[Example 2.5(a)]
	{watanabe:demazure-normal-graded} and then Gorenstein by
	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
	particular, this tells us a log spin canonical curve, the
	projectivization of a log spin canonical ring, is projectively
	Gorenstein.
\end{rem}

@@

\todo{Use Hilbert polynomial in an example}

@@

We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
\BQ$-divisor. Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.  Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$. Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.

\begin{defn}
\label{defn:lower-approximation}
\todo{Replace this notation with Hirzebruch--Jung fractions}
If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
\textbf{best lower approximation} to $\alpha$ if there does not
exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
\end{defn}

\begin{rem}
\label{rem:lower-approximation}
Note that all integers less than or equal to $\lfloor \alpha \rfloor$
are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
then the non-negative best lower approximations of
$\alpha$ form a finite sequence
\[
	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
\]

\noindent
Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
\end{rem}

\begin{figure}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha, \beta \in \BN$ such that
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
	N}.
\end{align}
Let
\[
	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$
{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
Then,

\begin{enumerate}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = k_i$ and $-\ord_P
	^{L'}(y_i) = c_i$.

@@

\sssec*{Idea of proof:}
The proof will be fairly involved. To show part (a), we first
define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$
with one generator corresponding to each positive best lower
approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch
to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
show that the set of elements we produce forms a basis.

@@

\noindent
Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

Let 
\[
	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
	\beta}
\]

\noindent
be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
\]
so the mediant inequality tells us
\[
	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
\]
Multiplying through by $k_i$ gives
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.

Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
\[
	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
\]

\noindent
which implies
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
\end{equation}

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j \cdot S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \bigcup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $\Bk[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in \Bk[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (\Bk[u,y_1, \ldots, y_n])$ as a $\Bk$-algebra.  That is, all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $\Bk[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$. Let $\halfcan$ be maximal such that $a_l\ne 0$.
Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
\[
b_j = \begin{cases}
	a_j &\text{ if } j \neq i\\
	a_j + 1 &\text{ if } j=i.
\end{cases}
\]

\noindent
Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.

@@

Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& \Bk[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).

>>>>

\noindent
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.

\end{defn}

@@

@@

We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
\BQ$-divisor. Whereas O'Dorney considers arbitrary $\BQ$-divisors in
$Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict
attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are
able to obtain much tighter bounds.  Moreover, Lemma ~\ref{lem:sat-1}
also extends to curves of genus $g > 0$. 
%Before stating Lemma
%~\ref{lem:sat-1}, we recall some theory from continued fractions.

%\begin{defn}
%\label{defn:lower-approximation}
%If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
%$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
%\textbf{best lower approximation} to $\alpha$ if there does not
%exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
%$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
%\end{defn}

%\begin{rem}
%\label{rem:lower-approximation}
%Note that all integers less than or equal to $\lfloor \alpha \rfloor$
%are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
%then the non-negative best lower approximations of
%$\alpha$ form a finite sequence
%\[
%	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \%alpha.
%\]
%
% proves 
%\begin{defn}\label{defn:cont-fract}
%Let $[a_1, \ldots, a_n]$ be the (Hirzebruch-Jung) continued fraction
%on $a_1, \ldots, a_n$ (given by $1 + \frac{1}{a_1+\frac{1}{... + \frac{1}{a_n}}}$).
%\end{defn}
%\begin{prop}\label{prop:primitives}
%The primitives 
%\end{prop}

%\noindent
%Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the posi%tive best lower approximations of $\alpha = \frac{14}{5}$.
%\end{rem}

\begin{figure}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}
\todo{Is this figure (figure 1)  still useful anywhere?}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha, \beta \in \BN$ such that $\frac{\alpha}{\beta}$ is reduced and
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
	N}.
\end{align}
%Let
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
%\]
%be the positive best lower approximations of $\frac{\alpha}{\beta}$
%{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
Then,

\begin{enumerate}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
	elements $y_1, \ldots, y_n$ where $\deg(y_i) = k_i<\beta$, $-\ord_P
	^{L'}(y_i) = c_i$ for some $k_i$'s and $c_i$'s such that $c_i<c_{i+1}\le \alpha$ and $k_i\le k_{i+1}\le \beta$ for all $i$.

@@

\sssec*{Idea of proof:}\todo{Update subsection}
The proof will be fairly involved. To show part (a), we first apply 
literature on continued fractions to 
define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
We then use Riemann--Roch
to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
show that the set of elements we produce forms a basis.

@@

\noindent
Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
\beta} \rfloor \}$.
This reduces the problem at hand to finding the primitives of the cone in $\mathbb{Z}\times \mathbb{Z}$ bounded by $y=0$ and $y=\frac{\alpha}{\beta}x$.

Literature on Cohn's geometric interpretation of hirzabruch jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).  Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be at most one new primitive, since we can construct points with $y$ coordinates between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in degree 1 and degree $k-1$, and these new primitives have pole order greater than all primitives of smaller $x$-coordinate.  Therefore, the ordering of primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values $k_i$'s are also in weakly increasing order.  Finally, let $y_1, \ldots, y_n$ be elements of $R_Lx$ with pole orders given by $c_1,\ldots, c_n$ and degrees given by the $x$ coordinates of the corresponding primitives.
%We will the use positive best lower approximations to
%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
%
%Let 
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
%	\beta}
%\]
%
%\noindent
%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
%\[
%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
%\]
%so the mediant inequality tells us
%\[
%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
%\]
%Multiplying through by $k_i$ gives
%\[
%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
%\]

%\noindent
%Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
%lower degrees. 
%Choose some $y_i \in(R_{
%\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
%
%Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
%\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
%best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
%\[
%	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
%\]
%
%\noindent
%which implies
%\begin{equation}\label{eqn:c-from-lower-terms}
%	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
%\end{equation}

We now recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j \cdot S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \bigcup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $\Bk[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in \Bk[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (\Bk[u,y_1, \ldots, y_n])$ as a $\Bk$-algebra.  That is, all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $\Bk[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$. Let $l$ be maximal such that $a_l\ne 0$.
Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
\[
b_j = \begin{cases}
	a_j &\text{ if } j \neq i\\
	a_j + 1 &\text{ if } j=i.
\end{cases}
\]

\noindent
Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S\cup S_0$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$. \todo{Check whether all these $S$ need to be changed to $S\cup S_0$ like here.}   
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S\cup S_0$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S\cup S_0$.

@@

Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ contains every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& \Bk[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
